The Next Release Problem in Real World

### 2018-12-16 PaperTitle.tex
Simulated Annealing and NSGA2 added (not finished)
ILP, result, graphs added
adding github account to author
Updates from ShareLaTeX

\usepackage{booktabs} % For formal tables

@@

@@

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings.
\end{abstract}

@@

\keywords{NRP, MONRP, Bugzilla}

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{graphicx}
\usepackage{subcaption}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\graphicspath{{images/}}

@@

\author{Jin-woo Lee}
\affiliation{%
    \institution{KAIST, 20120774}
}
\email{hiall21@kaist.ac.kr}

\author{Sue-hwan Lee}
\affiliation{%
    \institution{KAIST, 20110686}
}
\email{wwa098@kaist.ac.kr}

\begin{abstract}
This report provides the work of applying NRP problems to real-world problem. The NRP problem is where the company chooses which requirements to reflect when releasing the next version. We criticize the fact that most of the previous papers extracted results using random variables rather than actual data values. To improve that, we've taken the data out of the Bugzilla in Firefox and Eclipse repositories, and we've solved the problem of choosing which bugs need to be fixed in the next version. We compared performance by applying several known algorithms, SA, GA NSGA2, IHP, and AHP. This report shows how well the application of search-based algorithms to NRP problems in the real world, and which algorithms are the most effective.
\end{abstract}

@@

\keywords{NRP, MONRP, Bugzilla, Firefox, Eclipse}
